\section*{Introduction}
[PRG]

As with many animals, vision plays a key role in a number of behaviours performed by the fruitfly \emph{Drosophila melanogaster}, including mate-recognition \cite{Agrawal2014}, place homing \cite{Ofstad2011}, visual course control \cite{Borst2014}, collision-avoidance \cite{Tammero2002}, landing \cite{Tammero2002} and escaping a looming object (like a rolled newspaper, for example) \cite{Card2008}.
Of course \emph{Drosophila} are unique as the great range of neurogenetic techniques that are available give a realistic chance of understanding the neural circuits that underpin these visually guided behaviours. With that goal in mind, we investigate how small populations of well-described visual neurons in \emph{Drosophila} provide behaviourally relevant information.

In laboratory assays flies show interesting spontaneous visual behaviours. For instance, flies will orient towards bar stimuli (W. Reichardt, H. Wenking
Optical detection and fixation of objects by fixed flying flies
Naturwissenschaften, 56 (1969), pp. 424--425; K.G. G\"{o}tz
Course-control, metabolism and wing interference during ultralong tethered flight in Drosophila melanogaster
J. Exp. Biol., 128 (1987), pp. 35--46) and in a circular arena with two diametrically placed bars will walk between them for long periods. This spontaneous preference for elongated vertical bars is reduced as the bar is shortened until free flying flies show a spontaneous aversion to small cube stimuli (Maimon, G., Straw, A. D., \& Dickinson, M. H. (2008). A simple vision-based algorithm for decision making in flying Drosophila. Current Biology, 18(6), 464-470.). In addition to a suite of visual reflexes, \emph{Drosophila} also demonstrate complex visual behaviours involving interactions between orientation and memory.
For instance, there have been a number of papers investigating the process of pattern recognition and its neural underpinnings\cite{Pan2009,Liu2006,Ernst1999}.
The standard paradigm involves putting a fly into a closed-loop system where it is tethered in a drum, on the inside of which are two visual stimuli alternating every 90\degree\ (Fig.~\ref{fig:recap}E). As the fly attempts to rotate in one direction, the drum counter rotates, giving the illusion of closed-loop control. If the fly faces one of the patterns it receives negative reinforcement, a laser which heats the abdomen. Therefore over time if the fly is able to differentiate the patterns it will preferentially face the unpunished pattern. This procedure has been used to demonstrate that flies can differentiate stimulus pairs such as upright and inverted `T' shapes, a small and a large square, etc. \cite{Ernst1999}. That is, flies seem to possess a form of pattern recognition and pattern memory analogous to the better studied pattern memory of bees [HERE PUT 2/3 REFERENCES; Von Frisch, K. (1914). Der farbensinn und formensinn der biene. Zoologisches Jahrbucher, Physiologie, vol. 35 pp.1-188; Giurfa, M., \& Menzel, R. (1997). Insect visual perception: complex abilities of simple nervous systems. Current opinion in neurobiology, 7(4), 505-513.;Horridge, G. A. (2009). What Does the Honeybee See and how Do We Know?: A Critique of Scientific Reason. ANU E Press.].

The control of these visual behaviours is dependent on the central complex of flies, a brain area thought to be involved primarily in spatial representation and mediation between visual input and motor output \cite{Pfeiffer2014}.
The central complex comprises the ellipsoid body, the fan-shaped body, the paired noduli and the protocerebral bridge \cite{Young2010}.
This part of the brain has been characterised as the site of action selection and organisation and is claimed to be analogous/homologous to the basal ganglia in vertebrates \cite{Strausfeld2013}.
In the ellipsoid body, there are a class of neurons called `ring neurons', which are known to be involved in visual behaviours (R1: place homing \cite{Ofstad2011,Sitaraman2010,Sitaraman2008}; R2/R4m: pattern recognition \cite{Pan2009,Liu2006,Ernst1999}; R3/R4: bar fixation memory \cite{Neuser2008}).

Beyond the identification of brain regions associated with specific behaviours it is now possible to describe the properties of specific visual cells in the central complex. Seelig and Jayaraman \cite{Seelig2013} have studied two classes of ring neuron in the \emph{Drosophila} ellipsoid body.
The two subtypes of ring neuron investigated were the R2 and R4d ring neurons, of which only 28 and 14, respectively, were responsive to visual stimuli.
The cells were found to possess \acp{RF} that were large, centred in the ipsilateral portion of the visual field and with forms similar to those of mammalian simple cells \cite{Hubel1962}.
Like simple cells, many of these neurons showed strong orientation tuning and some were directionally sensitive.
The ring neuron \acp{RF}, however, are much coarser in form than simple cells, are far larger, are less evenly distributed across the visual field and respond mainly to orientations near the vertical.
This suggests that ring neurons might have a less generalistic function than simple cells (Wystrach, A., Dewar, A. D., \& Graham, P. (2014). Insect vision: Emergence of pattern recognition from coarse encoding. Current Biology, 24(2), R78-R80.). The population of simple cells ensures small high contrast boundaries of any orientation are detected at all points in the visual field. Thus the encoding provided by simple cells preserves visual information. Whereas the coarseness of the receptive fields of ring neurons, allied to the tight relationship between specific behaviours and sub-populations of ring neurons suggests that these cells are providing economical visual information in a behaviourally tuned way.

Here we advocate the use of a synthetic approach whereby investigations, in simulation, of the information provided by these populations of neurons can be related to behavioural requirements. We show how the popultion code is well-suited to the spontaneous bar orientation behaviours shown by flies. Similarly, we verify that our population of simulated ring neurons are able to discriminate visual patterns to the same standard as flies.
Upon deeper analysis, we demonstrate that certain shape parameters---`orientation', `size' and `elevation'---are implicit in the ring neurons' outputs to a high accuracy. Thus providing the information required for a suite of basic fly behaviours. Whereas the limited ability of ring neuron populations (and flies) in pattern discrimination casts doubt on more cognitive explanations of fly behaviour in pattern discrimination assays.
