\section*{Introduction}
As with many animals, vision plays a key role in a number of behaviours performed by the fruitfly \emph{Drosophila melanogaster}, including mate-recognition \cite{Agrawal2014}, place homing \cite{Ofstad2011}, visual course control \cite{Borst2014}, collision-avoidance \cite{Tammero2002}, landing \cite{Tammero2002} and escaping a looming object (like a rolled newspaper, for example) \cite{Card2008}.
Of course \emph{Drosophila} are unique as the great range of neurogenetic techniques that are available give a realistic chance of understanding the neural circuits that underpin these visually guided behaviours. With that goal in mind, we investigate how small populations of well-described visual neurons in \emph{Drosophila} provide behaviourally relevant information.

In addition to a suite of visual reflexes, \emph{Drosophila} also demonstrate complex visual behaviours involving interactions between orientation and memory.
For instance, there have been a number of papers investigating the process of pattern recognition and its neural underpinnings\cite{Pan2009,Liu2006,Ernst1999}.
The standard paradigm involves putting a fly into a closed-loop system where it is tethered in a drum, inside which are two visual stimuli alternating every 90\degree. As the fly attempts to rotate in one direction, the drum rotates in the other, giving the illusion of closed-loop control. If the fly faces one of the patterns it receives negative reinforcement, a laser which heats the abdomen. Therefore over time if the fly is able to differentiate the patterns it will preferentially face the unpunished pattern. This procedure has been used to demonstrate that flies can differentiate stimuli such as upright and inverted triangles, upright and inverted `T' shapes, a small and a large square, etc. \cite{Ernst1999}. That is, flies seem to possess a form of pattern memory.

Another classic behavioural paradigm for flies (bar fixation \cite{Neuser2008}) has been used to highlight other interesting visually guided behaviours.
Single flies are placed into a virtual-reality arena, with two vertical stripes shown 180\degree\ apart.
In this scenario, flies typically repeatedly head back and forth between the two bars.
Occasionally, however, the bars would disappear when a fly crossed the arena's midline and a new bar appeared at 90\degree\ to the old ones.
Flies responded by reorienting to this new target, which then also disappeared, whereupon flies resumed their initial heading, even though the original bars were still invisible. This indicates that directional information was stored in short-term memory.

The control of these visual behaviours is dependent on brain areas in the central complex of flies, a brain area thought to be involved primarily in spatial representation and mediation between visual input and motor output \cite{Pfeiffer2014}.
The central complex comprises the ellipsoid body, the fan-shaped body, the paired noduli and the protocerebral bridge \cite{Young2010}.
In the ellipsoid body, there are a class of neurons called `ring neurons', which are known to be involved in visual behaviours (R1: place homing \cite{Ofstad2011,Sitaraman2010,Sitaraman2008}; R2/R4m: pattern recognition \cite{Pan2009,Liu2006,Ernst1999}; R3/R4: bar fixation memory \cite{Neuser2008}).
Most of the ellipsoid body's connections, incoming and outgoing, are to the lateral accessory lobes and lateral triangle, though unfortunately little is known about more downstream targets \cite{Pfeiffer2014,Young2010}.
This part of the brain has been characterised as the site of action selection and organisation and is claimed to be analogous/homologous to the basal ganglia in vertebrates \cite{Strausfeld2013}.

A series of studies have identified the fine details of which parts of the central complex are involved in pattern recognition and short-term orientation memory.
Selective knock-out and activity staining of brain areas in the central complex has identified some of the details of the brain areas that support pattern recognition.
Both ring neurons and the fan-shaped body are known to be critical for this process, but whereas the fan-shaped body encodes two parameters of visual stimuli---`elevation' and `contour elevation'---in separate strata, R2 and R4m ring neurons store these parameters, as well as `size' and `vertical compactness', in a parameter-independent manner \cite{Pan2009}.
Interestingly, one parameter-independent mechanism for performing pattern recognition, retinotopic matching, has been shown to be a good model for fruitfly pattern recognition behaviour \cite{Dill1993}.
This mechanism would explain why pattern memories are invariant for vertical displacement \cite{Dill1993}, although not why this is not the case for horizontal displacement \cite{Tang2004}.
Short-term memory for visually defined headings has been shown to be dependent on the expression of a molecule involved in memory formation (S6 kinase II) in R3 and R4 ring neurons.
Mutant flies ($ign^{\emph{58/1}}$) without this expression reoriented towards the new bar in the bar fixation paradigm, but when it disappeared they did not turn to face their original direction.
When expression was restored in these flies, they would again reorient towards the (invisible) original bars' locations.

Beyond the identification of brain regions associated with specific behaviours we are now able to describe the properties of specific visual cells in the central complex. Seelig and Jayaraman \cite{Seelig2013} have studied two classes of ring neuron in the \emph{Drosophila} ellipsoid body.
The two subtypes of ring neuron investigated were the R2 and R4d ring neurons, of which only 28 and 14, respectively, were responsive to visual stimuli.
The cells were found to possess \acp{RF} that were large, centred in the ipsilateral portion of the visual field and with forms similar to those of mammalian simple cells \cite{Hubel1962}.
Like simple cells, many of these neurons showed strong orientation tuning and some were directionally sensitive.
The ring neuron \acp{RF}, however, are much coarser in form than simple cells, are far larger, are less evenly distributed across the visual field and respond mainly to orientations near the vertical.
This suggests that ring neurons may be tied to specific behaviours more than the general-purpose simple cells.
One possibility is that they are involved in homing towards large vertical bar-like objects, such as fruit trees, where adult \emph{Drosophila} feed and lay eggs.
R4 (and R3) neurons have previously been implicated in bar fixation memory (see above), and although no role has yet been suggested for R2 neurons in this regard, they have properties that would appear to make them suitable.

Here we advocate the use of a synthetic approach whereby investigations, in simulation, of the information provided by these small populations of neurons can be related to descriptions of behaviour. We verify that our population of simulated ring neurons are able to discriminate the visual patterns also discriminable by flies.
We then proceed to show that certain parameters---`orientation', `size' and `elevation'---are implicit in the ring neurons' outputs.
We argue, however, that although a neural network furnished with ring neuron-like cells as input can be trained to distinguish stimuli differing along a variety of pattern parameters, having a mechanism to extensively encode scenes in such parameter spaces is an unnecessary and computationally expensive means of performing this task.
Results are discussed in terms of sparse encoding, with reference to minimalist models of visual behaviour that have been applied to other insects.
