\section{Abstract}
All organisms wishing to survive and reproduce must be able to respond adaptively to a complex, changing world.
Yet the computational power available is constrained by biology and evolution, favouring mechanisms that are parsimonious yet robust.
Here we investigate the information carried in small populations of visually responsive neurons in \emph{Drosophila melanogaster}.
These small populations of so-called `ring neurons', projecting to the ellipsoid body of the central complex, are required for complex visual tasks.
Recently the receptive fields of these neurons have been mapped, allowing us to investigate what behaviours could be supported by these small population codes. These neurons have been implicated in behaviours such as pattern recognition and in a simulation of the classic pattern discrimination experiments, we show that the patterns of output from the small population of ring neurons matches observed fly behaviour. However, performance of the population code and the fly is not perfect. The pattern discrimination of the population of simulated ring neurons can be easily improved by the addition of extra neurons, suggesting this population is likely not tuned for recognising abstract shapes. Using artificial neural networks to ask how easy it is to decode stimulus information from the population code provided by ring neurons we showed that these small populations are well-suited for encoding information about size, position and orientation, which are more relevant behavioural parameters for a fly than abstract pattern properties. In this instance, computational modelling is key in investigating how perceptual circuits put information at the service of behaviour rather than how they preserve visual information.
